### 2014-04-14 paper/designspace.tex
small changes

\begin{figure}[t]
\centering
    \includegraphics[width=1.0\columnwidth]{figures/types.png}
\caption{Pipe openings: A shows a pair of \emph{open} pipes filled with copper paint to power an LED.  B shows an \emph{open} pipe with EL wire threaded through it.  C shows two \emph{semi-closed} pipes capped by rubber membranes.  In D, a rabbit has a \emph{fully enclosed} chamber to modify its weight.}
\label{fig:openings}
\end{figure}

@@

\subsection{Path Constraints}
Depending on the purpose of the pipe, its geometry may be constrained to specific locations within the 3D model. An \emph{endpoint-constrained} pipe requires specific start and end points, but the particular route of the internal path is flexible. This is the case for circuit schematics, where the electronic components have a fixed location, but many routing solutions are valid. In contrast, for a \emph{path-constrained} pipe the shape of the path is important. For example, threading electroluminescent (EL) wire through a clear pipe enables makers to emulate neon art (see Figure \ref{fig:openings}b) \bjoern{what happened to this subfigure? Kill reference if it's not coming back}. A \emph{fully constrained} pipe requires both specific terminals as well as a specific path. If a maker wishes the EL wire to exit the rear of the sign to hide the electronics, it requires a fully-constrained path (Figure \ref{fig:neon}). Finally, an \emph{unconstrained} pipe does not need a specific path or terminal points. A cavity to modify an object's weight is an example of an unconstrained pipe.

>>>>

\begin{figure}[t]
\centering
    \includegraphics[width=1.0\columnwidth]{figures/types.png}
\caption{Pipe openings: A shows a pair of \emph{open} pipes filled with copper paint to power an LED.  B shows two \emph{semi-closed} pipes capped by rubber membranes.  In C, a rabbit has a \emph{fully enclosed} chamber to modify its weight.}
\label{fig:openings}
\end{figure}

@@

\subsection{Path Constraints}
Depending on the purpose of the pipe, its geometry may be constrained to specific locations within the 3D model. An \emph{endpoint-constrained} pipe requires specific start and end points, but the particular route of the internal path is irrelevant. This is the case for circuit schematics, where the electronic components have a fixed location, but many routing solutions are valid. In contrast, for a \emph{path-constrained} pipe the shape of the path is important. For example, threading electroluminescent (EL) wire through a clear pipe enables makers to emulate neon art (see Figure \ref{fig:teaser}, right). A \emph{fully constrained} pipe requires both specific terminals as well as a specific path. If a maker wishes the EL wire to exit the rear of the sign to hide the electronics, she can use a fully-constrained path (Figure \ref{fig:neon}). Finally, an \emph{unconstrained} pipe does not need a specific path or terminal points. A cavity to modify an object's weight is an example of an unconstrained pipe.

### 2014-04-14 paper/discussion.tex
small changes

\emph{Visual} outputs can be mediated by gases, liquids, solid, particulates, or threadables.  Pneumatic actuation (as in PneUIs \cite{Yao-pneui} or Harrison's latex buttons \cite{Harrison-buttons}) can provides shape-changing interfaces if maelleable materials can be printed. 
%Gases carrying smoke also offer visual feedback. 
Air bubbles in liquids can also convey information~\cite{Heiner1999Percolator}. Splitting and mixing of colored liquids can be used as a display tactic; liquids can also be mixed in specific concentrations by servo-controlled gate structures as in Figure \ref{fig:direct}. %additionally mechanical motion can be fluid-mediated.

@@

Each of these properties could be used for object identification. As seen in Touch \& Activate \cite{Ono-touchandactivate}, different objects have different acoustic signatures.  As such, two objects that are visually identical but have differing internal chamber geometry may be distinguished acoustically.  Thus we can recall an object's identity once its acoustic signature has been recorded.  Similarly, the Touch\'{e} system \cite{Sato-touche} relies on distinguishing \emph{capacitive} signatures of objects, both in static states and as their boundary conditions are changed by human interaction. Weight could also be used as a simple metric of object identity, but would be less distinctive than acoustic or capacitive signatures.

>>>>

\emph{Visual} outputs can be mediated by gases, liquids, solid, particulates, or threadables.  Pneumatic actuation (as in PneUIs \cite{Yao-pneui} or Harrison's latex buttons \cite{Harrison-buttons}) provides shape-changing interfaces if maelleable materials can be printed. 
%Gases carrying smoke also offer visual feedback. 
Air bubbles in liquids can also convey information~\cite{Heiner1999Percolator}. Splitting and mixing of colored liquids can be used as a display tactic; liquids can also be mixed in specific concentrations by servo-controlled gate structures as in Figure \ref{fig:direct}. %additionally mechanical motion can be fluid-mediated.

@@

Each of these properties could be used for object identification. As seen in Touch \& Activate \cite{Ono-touchandactivate}, different objects have different acoustic signatures.  As such, two objects that are visually identical but have differing internal chamber geometry may be distinguished acoustically.  Thus we can recall an object's identity once its acoustic signature has been recorded.  Similarly, the Touch\'{e} system \cite{Sato-touche} relies on distinguishing \emph{capacitive} signatures of objects, both in static states and as their boundary conditions are changed by human interaction. Weight could also be used as a simple metric of identity, but is less distinctive than acoustic or capacitive signatures.

### 2014-04-14 paper/exampleobjects.tex
bjoern's pass
small changes

\section{Totally Tubular Example Objects}
To evaluate and highlight our tool's capabilities, we fabricated a set of five prototype objects designed using \systemnamenospace.  To show that our approach is printer-independent, we fabricated some on a Makerbot Replicator 2 and the rest on an Objet Connex 260.  Each prototype object explores the expansion of an existing sensing or actuation technique to the surface of 3D printed objects.
%All prototypes were fabricated in a single piece, unless described otherwise. \bjoern{2 of 5 will have been fabricated otherwise -  Radio, Neon sign - both in pieces.}

@@

\subsection{Custom Radio (open, threadable, endpoint)}
A custom radio (Figure \ref{fig:examples}c) shows how pipes can be used to integrate electronic components into the user-facing surface of an object. The radio includes a power and volume dial, and LED which goes on when the radio is on, and a tuner dial. An Arduino Pro Micro microcontroller, Si4703 FM tuner, and 6V (4xAA) power supply are embedded in the base of the radio. The sound is played through a single .5 Watt speaker. This shows a Midas-like \cite{Savage-midas} possibility : multiple terminals all routed back to a shared endpoint (in this case, the Arduino). \bjoern{last sentence is confusing. May not need Midas reference.}

@@

The maze is based on an SVG file we manually created and processed with our internal path routing tool.  We printed the maze on the Objet using a transparent material \bjoern{bottom doesn't look transparent. The final artifact was fabricated in two halves fastened together via glue, to allow removal of support material with a high-pressure water tool.  We plugged the ends of the tubes post-print with additional material to ensure the ball does not escape.

>>>>

\section{Totally Tubular Example Objects}
To evaluate and highlight our tool's capabilities, we fabricated a set of six prototype objects designed using \systemnamenospace.  To show that our approach is printer-independent, we fabricated some on a Makerbot Replicator 2 and the rest on an Objet Connex 260.  Each prototype object explores the expansion of an existing sensing or actuation technique to the surface of 3D printed objects.
%All prototypes were fabricated in a single piece, unless described otherwise. \bjoern{2 of 5 will have been fabricated otherwise -  Radio, Neon sign - both in pieces.}

@@

\subsection{Custom Radio (open, threadable, endpoint)}
A custom radio (Figure \ref{fig:examples}c) shows how pipes can be used to integrate electronic components into the user-facing surface of an object. The radio includes a power and volume dial, and LED which goes on when the radio is on, and a tuner dial. An Arduino Pro Micro microcontroller, Si4703 FM tuner, and 6V (4xAA) power supply are embedded in the base of the radio. The sound is played through a single .5 Watt speaker.

@@

The maze is based on an SVG file we manually created and processed with our internal path routing tool.  We printed the maze on the Objet using a transparent material \bjoern{bottom doesn't look transparent}. The final artifact was fabricated in two halves fastened together via glue, to allow removal of support material with a high-pressure water tool.  We plugged the ends of the tubes post-print with additional material to ensure the ball does not escape.

### 2014-04-14 paper/introduction.tex
small changes

\section{Introduction}
Makers, researchers, and professional designers (jointly "makers" for the remainder of this paper) increasingly leverage 3D printers as tools for design work.  A wide array of objects, ranging from toy figurines to video game controllers and jet engine blades, are now prototyped (and sometimes even manufactured) using these machines.  Most models fabricated on 3D printers today are passive: they express the form, but not the function, of an object.

@@

This paper introduces a novel technique involving the removal of material from the interior of 3D models, prior to printing, to create pipes and other cavities.  These pipes can be filled, post-print, with a variety of media that enable input, display, and tactile feedback.  This {\em subtractive} approach is complementary to {\em additive} approaches that inject custom print materials, such as conductors, during the actual printing process \cite{Sells-reprap}. While our approach requires some manual assembly after a print completes, it gives makers the opportunity to cheaply and rapidly prototype a diverse range of interactive objects on 3D printers, including popular single-material fused-deposition modeling machines (Figure \ref{fig:teaser}).

>>>>

\section{Introduction}
Makers, researchers, and professional designers (jointly ``makers" for the remainder of this paper) increasingly leverage 3D printers as tools for design work.  A wide array of objects, ranging from toy figurines to video game controllers and jet engine blades, are now prototyped (and sometimes even manufactured) using these machines.  Most models fabricated on 3D printers today are passive: they express the form, but not the function, of an object.

@@

This paper introduces a novel technique involving removing material from the interior of 3D models, prior to printing, to create pipes and other cavities.  These pipes can be filled, post-print, with a variety of media to enable input, display, and tactile feedback.  This {\em subtractive} approach is complementary to {\em additive} approaches that inject custom print materials, such as conductors, during the actual printing process \cite{Sells-reprap}. While our approach requires some manual assembly after a print completes, it gives makers the opportunity to cheaply and rapidly prototype a range of interactive objects on 3D printers, including popular single-material fused-deposition modeling machines (colored objects in Figure \ref{fig:teaser}).
